### 2015-01-06 paper/paper.tex
autocommit 01/06 23:54
autocommit 01/06 23:55
autocommit 01/06 23:58

\begin{figure}
	\begin{subfigure}{0.4\columnwidth}
		\centering
		\includegraphics[width=\columnwidth]{order/2_threads.png}
		\label{fig:order:2_threads}
		\caption{HDA* 2 threads}
	\end{subfigure}
	\begin{subfigure}{0.4\columnwidth}
		\centering
		\includegraphics[width=\columnwidth]{order/4_threads.png}
		\label{fig:order:4_threads}
		\caption{HDA* 4 threads}
	\end{subfigure}
	\begin{subfigure}{0.4\columnwidth}
		\centering
		\includegraphics[width=\columnwidth]{order/8_threads.png}
		\label{fig:order:8_t8hreads}
		\caption{HDA* 8 threads}
	\end{subfigure}
	\begin{subfigure}{0.4\columnwidth}
		\centering
		\includegraphics[width=\columnwidth]{order/delay.png}
		\label{fig:order:delay}
		\caption{delayed expanding HDA*}
	\end{subfigure}
	\label{fig:hdastar_orders}
	\caption{HDA*の探索順}
\end{figure}%

@@

\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{eps/efficiency.pdf}	
	\label{fig:david_speedup}
	\caption{Efficiency of HDA*}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{eps/search_overhead.pdf}	
	\label{fig:david_so}
	\caption{Search Overhead of HDA*}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{width=0.4\columnwidth}
		\includegraphics[width=\columnwidth]{eps/hdastar_tuning_walltime.pdf}
		\label{fig:hdastar_tuning_walltime}
	\end{subfigure}
	\begin{subfigure}{width=0.4\columnwidth}
		\includegraphics[width=\columnwidth]{eps/hdastar_tuning_expd.pdf}
		\label{fig:hdastar_tuning_expd}
	\end{subfigure}
	\label{fig:hdastar_tuning}
	\caption{zobrist vs haive hash, vector vs heap open list}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.4\columnwidth]{speedup/safepbnf-8_tuning.png}
	\label{fig:pbnf_tuning}
	\caption{Tuning PBNF}
\end{figure}
\begin{figure}
	\centering
	\begin{subfigure}{width=0.4\columnwidth}
		\includegraphics[width=\columnwidth]{eps/safepbnf_tuning_walltime.pdf}
		\label{fig:safepbnf_tuning_walltime}
	\end{subfigure}
	\begin{subfigure}{width=0.4\columnwidth}
		\includegraphics[width=\columnwidth]{eps/safepbnf_tuning_expd.pdf}
		\label{fig:safepbnf_tuning_expd}
	\end{subfigure}
	\label{fig:safepbnf_tuning}
	\caption{vector vs heap}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth]{eps/15puzzle_vector_walltime.pdf}
		\label{fig:15puzzle_vector}
		\caption{15 Puzzle with vector open list}
	\end{subfigure}

	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth]{speedup/15puzzle_heap.png}
		\label{fig:15puzzle_vector}
		\caption{15 Puzzle with heap open list}
	\end{subfigure}

	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth]{speedup/grid.png}
		\label{fig:grid}
		\caption{Grid Pathfinding}
	\end{subfigure}

	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_20_mst_bug.png}
		\label{fig:tsp_20_mst}
		\caption{TSP with minimum spanning tree (20 cities)}
	\end{subfigure}

	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_13_roundtrip_bug.png}
		\label{fig:tsp_13_round}
		\caption{TSP with Round-trip distance (13 cities)}
	\end{subfigure}

	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_13_blind_bug.png}
		\label{fig:tsp_13_blind}
		\caption{TSP with blind (13 cities)}
	\end{subfigure}
	\label{fig:comparison}
	\caption{HDA*とPBNFの実行速度の比較}
\end{figure}%

>>>>

\begin{figure}
	\begin{subfigure}{0.6\columnwidth}
		\centering
		\includegraphics[width=\columnwidth]{order/2_threads.png}
		\label{fig:order:2_threads}
		\caption{HDA* 2 threads}
	\end{subfigure}
	\begin{subfigure}{0.6\columnwidth}
		\centering
		\includegraphics[width=\columnwidth]{order/4_threads.png}
		\label{fig:order:4_threads}
		\caption{HDA* 4 threads}
	\end{subfigure}
	\begin{subfigure}{0.6\columnwidth}
		\centering
		\includegraphics[width=\columnwidth]{order/8_threads.png}
		\label{fig:order:8_t8hreads}
		\caption{HDA* 8 threads}
	\end{subfigure}
	\begin{subfigure}{0.6\columnwidth}
		\centering
		\includegraphics[width=\columnwidth]{order/delay.png}
		\label{fig:order:delay}
		\caption{delayed expanding HDA*}
	\end{subfigure}
	\label{fig:hdastar_orders}
	\caption{HDA*の探索順}
\end{figure}%

@@

\begin{figure}
	\centering
	\includegraphics[width=0.6\columnwidth]{eps/efficiency.pdf}	
	\label{fig:david_speedup}
	\caption{Efficiency of HDA*}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.6\columnwidth]{eps/search_overhead.pdf}	
	\label{fig:david_so}
	\caption{Search Overhead of HDA*}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth]{eps/hdastar_tuning_walltime.pdf}
		\label{fig:hdastar_tuning_walltime}
	\end{subfigure}
	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth]{eps/hdastar_tuning_expd.pdf}
		\label{fig:hdastar_tuning_expd}
	\end{subfigure}
	\label{fig:hdastar_tuning}
	\caption{zobrist vs haive hash, vector vs heap open list}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth]{eps/safepbnf_tuning_walltime.pdf}
		\label{fig:safepbnf_tuning_walltime}
	\end{subfigure}
	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth]{eps/safepbnf_tuning_expd.pdf}
		\label{fig:safepbnf_tuning_expd}
	\end{subfigure}
	\label{fig:safepbnf_tuning}
	\caption{vector vs heap}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth]{eps/15puzzle_vector_walltime.pdf}
		\label{fig:15puzzle_vector}
		\caption{15 Puzzle with vector open list}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth]{eps/15puzzle_heap_walltime.pdf}
		\label{fig:15puzzle_vector}
		\caption{15 Puzzle with heap open list}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth]{eps/grid_walltime.pdf}
		\label{fig:grid}
		\caption{Grid Pathfinding}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_20_mst_walltime.png}
		\label{fig:tsp_20_mst}
		\caption{TSP with minimum spanning tree (20 cities)}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_13_roundtrip_walltime.png}
		\label{fig:tsp_13_round}
		\caption{TSP with Round-trip distance (13 cities)}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_13_blind_walltime.png}
		\label{fig:tsp_13_blind}
		\caption{TSP with blind (13 cities)}
	\end{subfigure}
	\label{fig:comparison}
	\caption{HDA*とPBNFの実行速度の比較}
\end{figure}%

\begin{figure}
	\centering
	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth]{eps/15puzzle_vector_expd.pdf}
		\label{fig:15puzzle_vector}
		\caption{15 Puzzle with vector open list}
	\end{subfigure}

	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth]{eps/15puzzle_heap_expd.pdf}
		\label{fig:15puzzle_vector}
		\caption{15 Puzzle with heap open list}
	\end{subfigure}

	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth]{eps/grid_expd.pdf}
		\label{fig:grid}
		\caption{Grid Pathfinding}
	\end{subfigure}

	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_20_mst_expd.png}
		\label{fig:tsp_20_mst}
		\caption{TSP with minimum spanning tree (20 cities)}
	\end{subfigure}

	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_13_roundtrip_expd.png}
		\label{fig:tsp_13_round}
		\caption{TSP with Round-trip distance (13 cities)}
	\end{subfigure}

	\begin{subfigure}{0.4\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_13_blind_expd.png}
		\label{fig:tsp_13_blind}
		\caption{TSP with blind (13 cities)}
	\end{subfigure}
	\label{fig:comparison}
	\caption{HDA*とPBNFの探索ノード数の比較}
\end{figure}%
